---
title: "Step 1: Just R markdown"
output: 
  html_document:
    theme: journal 
---

###Rmarkdown is Very Easy
In R Studio all you need to do is: 

*  File > New File >  R Markdown > Choose Default Output Format > 'html'
*  make sure your *yaml* header (the thing at the top of the .rmd file) is ok 
*  type some stuff in the space below the header
*  then you can 'Knit' or print your html document via the button on the toolbar in R Studio or via **ctrl + shift + k**


###You create content via 'chunks'

* you can the include code used in the final html doc

```{r chunk 1, warning=FALSE}
library(tidyverse)
library(ggthemes)

# dataframe with econ stats in it 

df <- longley

# making simple line graph

ggplot(df, aes(Year, Armed.Forces)) + 
  geom_line() + 
    theme_bw()


```

*  or not not include it

```{r chunk no code, echo=FALSE}
library(tidyverse)
library(ggthemes)

# dataframe with econ stats in it 

df <- longley

# making simple line graph

ggplot(df, aes(Year, Armed.Forces)) + 
  geom_line() + 
    theme_bw()


```



