---
title: "Dashboard Example"
output: 
  flexdashboard::flex_dashboard:
    vertical_layout: scroll
    theme: journal
---
```{r setup and data import, echo=FALSE, warning=FALSE, include=FALSE}

# Reading relevant packages
#  Note that i am not including the below code in via 'include = FALSE'

library(tidyverse)
library(ggthemes)
library(viridis)
library(corrplot)
library(sjPlot)


# dataframe with econ stats in it 

df <- longley %>% 
  mutate(GNP.adj = (GNP/GNP.deflator)*100)


# generating input dataset for bar plot of 1950s population levels

plot.input <- df %>% select(Year, Unemployed, Employed, Armed.Forces, Population) %>% 
      gather(., pop.type, pop.num, -Year) 

# generating input dataset for growth plots
#    calcualting nominal (growth) and real growth (growth.adj) rates

growth.input <- df %>% 
  mutate(
    growth = (GNP - lag(GNP)) / lag(GNP),
    growth.adj = (GNP.adj - lag(GNP.adj)) / lag(GNP.adj)) %>% 
      drop_na(growth)


```


Exploratory Analysis
=====================================  

Inputs {.sidebar}
-----------------------------------------------------------------------

From this poorly assembled data I think that: 

*  There may be an intriguing relationship **between the population of the armed forces and GNP**
*  I wil try to explore this on the next page

Column 
------------------------------------- 

```{r area chart, echo = FALSE, warning=FALSE}
# Stacked Area Chart 
ggplot(plot.input, aes(Year, pop.num)) +
  geom_area(aes(fill = pop.type), alpha = .5) + 
  scale_fill_viridis(discrete = TRUE) + 
  scale_x_continuous(breaks = c(seq(min(plot.input$Year), max(plot.input$Year)))) + 
      ggtitle("it changes! again") + 
      theme_bw() +
        theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


Column {.tabset}
-------------------------------------

### GNP Over Time

```{r nominal and adj gnp, echo=FALSE, warning=FALSE}
# making line plot of gnp over time w/ both real and nominal gnp 

ggplot(growth.input) + 
  geom_line(aes(Year, GNP), size = 1) + 
  geom_line(aes(Year, GNP.adj), size = 1, linetype = "dashed") + 
       scale_x_continuous(breaks = c(seq(min(growth.input$Year), max(growth.input$Year)))) + 
  ggtitle("GNP over time") + 
        theme_bw()
```  

### Nominal Growth Rate

```{r nominal growth, echo=FALSE, warning=FALSE}
# line plot of nominal growth rate

ggplot(growth.input) + 
  geom_line(aes(Year, growth), size = 1) + 
    scale_y_continuous(breaks = c(-0.1, 0, .1, .2, .3), limits = c(-0.1, .3),
                       labels = scales::percent) + 
       scale_x_continuous(breaks = c(seq(min(growth.input$Year), max(growth.input$Year)))) + 
  ggtitle("Growth: Not Adjusted For Infaltion") + 
        theme_bw()
  
```

### Inflation-adj. Growth 

```{r adj growth, echo=FALSE, warning=FALSE}
#line plot of real growth rate 

ggplot(growth.input, aes(Year, growth.adj)) + 
  geom_line( size = 1 ) + 
  geom_smooth(fill = "grey70", linetype = 0, method = "lm" ) + 
  scale_y_continuous(breaks = c(-0.1, 0, .1, .2), limits = c(-0.1, .2),
                   labels = scales::percent) + 
       scale_x_continuous(breaks = c(seq(min(growth.input$Year), max(growth.input$Year)))) + 
   ggtitle("Growth: Adjusted For Infaltion") + 
        theme_bw()

```

Regression Analysis
=====================================  

Column 
------------------------------------- 

### Correlation Matrix

```{r, echo=FALSE, warning=FALSE}

# Using original 'wide' dataset to build correlation matrix
# note echo is set to 'FALSE' so the plot will print but not the code

# creating correlation matrix
df.cor <- cor(df)

# creating correlation matrix figure w. package corrplot 
corrplot(df.cor, method = "number", type = "lower")

```

Column {.tabset}
------------------------------------- 

### Model Results 
```{r model selection, echo=FALSE}
# making a dumb multiple regression model and then printing graphic results via sjPlot

# multiple regression
model_example <- lm(GNP.adj ~ Year + Population + Armed.Forces + Unemployed, data = df)


# regression results 
sjPlot::plot_model(model_example)


```

### Model Diagnostics: Residuals
```{r model diagnostics, echo=FALSE}

# residual diagnostics for dumb model plotted using sjPlot, note type = "residual" 

sjPlot::plot_model(model_example, type = "resid")

```

Assessment {.sidebar}
-----------------------------------------------------------------------
The correlation matrix shows that many potential independent variables are correlated to each other. This may endanger any mutiple regression! I am terrified! But we do it anyway!!! Reisudals appear very biased and standard error is large for the estimators. I remain afraid. Good thing I presented my misguided analysis clearly. 



